---
title: "Emogo Combined Analysis"
author: "Rista Plate via Martin Zettersten"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_depth: 2
    toc_float: yes
---


```{r setup, include=FALSE}
library(here)
library(tidyverse)
library(ggplot2)
library(viridisLite)
library(lme4)
library(ggstance)
library(cowplot)
library(AICcmodavg)
```

# Data Processing

## Read in data

```{r}
d_v1 <- read_csv("emogo-v1-alldata-anonymized.csv") %>%
  mutate(task_version = "v1")

d_v2 <- read_csv("emogo-v2-alldata.csv") %>%
  mutate(task_version = "v2")

d_pers <- read_csv("emogo-spark-personality-alldata-anonymized.csv") %>%
  mutate(task_version = "spark-personality")

d_psych <- read_csv("emogo-spark-psychopathology-alldata-anonymized.csv") %>%
  mutate(task_version = "spark-psychopathology")

d <- d_v1 %>%
  full_join(d_v2) %>%
  full_join(d_pers) %>%
  full_join(d_psych)


d <- d %>%
  filter(
    !(trial_type %in% c("show-reward"))
  )

length(unique(d$subject))
```

## Adding some useful columns

Adding columns to characterize participant choices.

```{r}
d <- d %>%
  mutate(
    trial_number = case_when(
      trial_index<8 ~ trial_index,
      trial_index<199 ~ 7+(trial_index-7)/2,
      TRUE ~ trial_index-96
    )
  ) %>%
  relocate(trial_number,.after=trial_index) %>%
  mutate(
    test_trial_number = case_when(
      trial_number<7 ~ NA_real_,
      trial_number<103 ~ trial_number-6,
      TRUE ~ NA_real_
    )
  ) %>%
  relocate(test_trial_number,.after=trial_number) %>%
  mutate(
    block_trial_number = case_when(
      test_trial_number < 49 ~ test_trial_number,
      TRUE ~ test_trial_number - 48),
    block_trial_number_c = block_trial_number - 24.5
  ) %>%
  relocate(block_trial_number,.after=test_trial_number) %>%
  relocate(block_trial_number_c,.after=block_trial_number) %>%
  mutate(
    explore_block = case_when(
      test_trial_number<9 ~ 1,
      test_trial_number<17 ~ 2,
      test_trial_number<25 ~ 3,
      test_trial_number<33 ~ 4,
      test_trial_number < 41 ~ 5,
      test_trial_number < 49 ~ 6,
      test_trial_number < 57 ~ 7,
      test_trial_number<65 ~ 8,
      test_trial_number<73 ~ 9,
      test_trial_number<81 ~ 10,
      test_trial_number <89 ~ 11,
      test_trial_number <97 ~ 12,
      TRUE ~ NA_real_
    )
  ) %>%
  mutate(
    max_reward_choice = case_when(
      reward_score_unadjusted ==8 ~ 1,
      !is.na(test_trial_number) ~ 0,
      TRUE ~ NA_real_
    )
  ) %>%
  mutate(
    cur_structure_condition=case_when(
      test_trial_number < 49 ~ structure_condition,
      !is.na(test_trial_number) & match_condition == "match" ~ structure_condition,
       test_trial_number >= 49 & structure_condition == "emotion" ~ "model",
      test_trial_number >= 49 & structure_condition == "model" ~ "emotion"
    )
  ) %>%
  mutate(block = case_when(
      test_trial_number < 49 ~ 1,
      test_trial_number >= 49 ~ 2,
      TRUE ~ NA_real_
    ))

#recenter vars
d <- d %>%
  mutate(
    structure_condition_c = case_when(
      structure_condition == "model" ~ -0.5,
      structure_condition == "emotion" ~ 0.5),
    cur_structure_condition_c = case_when(
      cur_structure_condition == "model" ~ -0.5,
      cur_structure_condition == "emotion" ~ 0.5),
    match_condition_c = case_when(
      match_condition == "match" ~ 0.5,
      match_condition == "mismatch" ~ -0.5
    ),
    cur_structure_condition_model = case_when(
      cur_structure_condition == "model" ~ 0,
      cur_structure_condition == "emotion" ~ 1),
    cur_structure_condition_emotion = case_when(
      cur_structure_condition == "model" ~ -1,
      cur_structure_condition == "emotion" ~ 0),
    match_condition_match = case_when(
      match_condition == "match" ~ 0,
      match_condition == "mismatch" ~ -1
    ),
    match_condition_mismatch = case_when(
      match_condition == "match" ~ 1,
      match_condition == "mismatch" ~ 0
    ),
    block_c = case_when(
      test_trial_number < 49 ~ -0.5,
      TRUE ~ 0.5
    ),
    block_learn = case_when(
      block==1 ~ 0,
      block==2 ~ 1
    ),
    block_gen = case_when(
      block==1 ~ -1,
      block==2 ~ 0
    )
  )
```

## Check data {.tabset}


### Open ended responses

```{r}
open_resps <- d %>%
  filter(grepl("patterns",response)) %>%
  select(subject, structure_condition, match_condition ,response) %>% 
  extract(response, into = c("patterns", "strategy", "comments"),
          regex = "patterns\":\"(.*)\",\"strategy\":\"(.*)\",\"comments\":\"(.*)")

#write_csv(open_resps, "emogo_combined_open_resps.csv")
```


### Attention check

```{r}
attention_check <- d %>%
  filter(trial_index %in% c(4,5)) %>%
  mutate(
    attention_check_correct_choice = case_when(
      trial_index == 4 ~ "stimuli/horse.jpg",
      trial_index == 5 ~ "stimuli/hammer.jpg"
    ),
    check_correct = ifelse(attention_check_correct_choice==choiceImage,1,0)
  ) %>%
  group_by(subject) %>%
  summarize(
    N=n(),
    avg_correct = mean(check_correct)
  )

passed_attention_check <- attention_check %>%
  filter(avg_correct ==1) %>%
  pull(subject)
```

### Total time

```{r}
total_time <- d %>%
  filter(trial_index==206) %>%
  select(subject,time_elapsed) %>%
  distinct() %>%
  mutate(time_mins = time_elapsed/1000/60)

#Minumum time
min(total_time$time_mins)

#Any subjects with times under 4 minutes?
subjects_too_fast <- total_time %>%
  filter(time_mins<4)

subjects_too_fast %>%
  pull(subject)
```

### Check image location selection

```{r}
percent_location_selections <- d %>%
  filter(!is.na(test_trial_number)) %>%
  group_by(subject,choiceLocation) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

#any frequencies above 80%?
subjects_same_location_exclusion <- percent_location_selections %>%
  filter(freq>0.8) 

subjects_same_location_exclusion %>%
  distinct(subject) %>%
  pull(subject)
```

### Reward ranks

```{r}
reward_rank <- d %>%
  filter(subject %in% passed_attention_check) %>%
  filter(test_trial_number==96) %>%
  select(subject,structure_condition,match_condition,score_after_trial)

median_score <- median(reward_rank$score_after_trial)

ggplot(reward_rank,aes(x=score_after_trial))+
  geom_histogram()+
  geom_vline(xintercept = median_score)

ggplot(reward_rank,aes(x=score_after_trial,color=match_condition))+
  geom_density()+
  facet_wrap(~structure_condition)

subjects_top_50 <- reward_rank %>%
  filter(score_after_trial>=median_score) %>%
  select(subject)

#write_csv(subjects_top_50,here("data-analysis","data","v1","processed","subjects_top_50.csv"))

conditions_top_50 <- reward_rank %>%
  filter(subject %in% subjects_top_50$subject) %>%
  group_by(structure_condition,match_condition) %>%
  tally()
conditions_top_50
```

### Final tally

```{r}
#exclude any participants who meet exclusion criteria
d <- d %>%
  filter(subject %in% passed_attention_check) %>%
  filter(!(subject %in% subjects_same_location_exclusion)) %>%
  filter(!(subject %in% subjects_too_fast))

d %>%
  distinct(subject,structure_condition,match_condition) %>%
  group_by(structure_condition,match_condition) %>%
  tally()
```

# SRCD


## Emotion
```{r}
d_graph <- d %>%
  filter(test_trial_number < 49)%>%
  mutate(choiceValence = ifelse(choiceEmotion == "CC" | choiceEmotion == "HE" | choiceEmotion == "HO" | choiceEmotion == "SUR", "positive emotions (calm, happy, exuberent, surprise)", "negative emotions (anger, fear, disgust, sad")) %>%
  mutate(choiceGender = ifelse(grepl('M',choiceModel), "male", "female")) %>%
  mutate(choiceRace = ifelse(grepl('A',choiceModel),"Asian",
                             ifelse(grepl('B',choiceModel),"Black",
                                    ifelse(grepl('H',choiceModel),"Hispanic", "White")))) %>%
  mutate(choiceValence_C = ifelse(choiceValence ==  "positive emotions (calm, happy, exuberent, surprise)", .5, -.5))
  
d_get_reward_emo <- d_graph %>%
  filter(structure_condition == "emotion") %>%
  filter(reward_score_unadjusted == 8) %>%
  mutate(rewEmotion = choiceEmotion) %>%
  distinct(subject, task_version, rewEmotion)

d_graph_emotion <- d_graph %>%
  full_join(d_get_reward_emo) %>%
  mutate(rewEmotion = ifelse(grepl('AO',rewEmotion),"angry",
                           ifelse(grepl('CC',rewEmotion),"calm",
                           ifelse(grepl('DO',rewEmotion),"disgust",
                           ifelse(grepl('FO',rewEmotion),"fear",
                           ifelse(grepl('HE',rewEmotion),"exuberent",
                           ifelse(grepl('HO',rewEmotion),"happy",
                           ifelse(grepl('SC',rewEmotion),"sad","surprise")))))))) %>%
  mutate(rewEmotion_inclModel = ifelse(d_graph$structure_condition == "model", "model", rewEmotion)) %>%
 drop_na(rewEmotion_inclModel) %>%
  mutate(rewEmoValence = ifelse(rewEmotion_inclModel == "model", "model",
         ifelse(rewEmotion == "calm" | rewEmotion == "exuberent" | rewEmotion == "happy" | rewEmotion == "surprise", "positive emotions (calm, happy, exuberent, surprise)", "negative emotions (anger, fear, disgust, sad)"))) %>%
  mutate(rewEmoHAPPY_EX = ifelse(rewEmotion_inclModel == "model", "model",
                                 ifelse(rewEmotion == "exuberent" | rewEmotion == "happy" , "happy emotions (happy, exuberent)", "not happy emotions")) )

length(unique(d_graph_emotion$subject))
table(d_graph_emotion$rewEmotion_inclModel)

color1 <- "#2B959A"
color2 <-"#D6692A"

ggplot(d_graph_emotion,aes(test_trial_number,max_reward_choice,color = structure_condition))+
  geom_jitter(height = .005, alpha = .05)+
  geom_smooth(method = "loess")+
  theme_bw()+labs(x="Trial Number",y="Chose Best Option")+
  scale_color_manual(values=c(color1, color2), labels=c("Emotion","Model"),name="Structure Condition")+
  theme(panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.line = element_line(colour = "black"), legend.key.size = unit(1, "cm"),text=element_text(size=20, family="Times"))


ggplot(d_graph_emotion,aes(test_trial_number,max_reward_choice,color = rewEmotion_inclModel))+
  geom_jitter(height = .005, alpha = .05)+
  geom_smooth(method = "loess")+
  geom_smooth(method = "loess")+
  theme_bw()+labs(x="Trial Number",y="Chose Best Option")+
  #scale_color_manual(name="Structure Condition")+
  theme(panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.line = element_line(colour = "black"), legend.key.size = unit(1, "cm"),text=element_text(size=20, family="Times"))

ggplot(d_graph_emotion,aes(test_trial_number,max_reward_choice,color = rewEmotion_inclModel))+
  geom_jitter(height = .005, alpha = .05)+
  geom_smooth(method = "loess")+
  xlab("Trial Number")+
  ylab("chose best option")+
  facet_grid(~ rewEmotion_inclModel) +
  theme_bw()+labs(x="Trial Number",y="Chose Best Option")+
  #scale_color_manual(name="Structure Condition")+
  theme(panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  legend.position = "none",
  axis.line = element_line(colour = "black"), legend.key.size = unit(1, "cm"),text=element_text(size=20, family="Times"))
  
ggplot(d_graph_emotion,aes(test_trial_number,max_reward_choice,color = rewEmoValence))+
  geom_jitter(height = .005, alpha = .05)+
  geom_smooth(method = "loess")+
  scale_color_manual(values = c("blue", "darkred", "darkgreen"))+
  xlab("Trial Number")+
  ylab("chose best option") 

ggplot(d_graph_emotion,aes(test_trial_number,max_reward_choice,color = rewEmoHAPPY_EX))+
  geom_jitter(height = .005, alpha = .05)+
  geom_smooth(method = "loess")+
  theme_bw()+labs(x="Trial Number",y="Chose Best Option")+
  scale_color_manual(values=c("darkgreen", "blue", "darkred"), labels=c("Happy & Exhuberent","Model", "All Other Emotions"),name=" ")+
  theme(panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.line = element_line(colour = "black"), legend.key.size = unit(1, "cm"),text=element_text(size=20, family="Times"))
```

```{r}
m <- glmer(max_reward_choice ~ cur_structure_condition_c*block_trial_number_c + (1+block_trial_number_c|subject)+(1|choiceImage),data=d_graph, family=binomial,glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)))
summary(m)

plot_model(m, type = "pred", terms = c("block_trial_number_c", "cur_structure_condition_c"))

m_emotion_val <- glmer(max_reward_choice ~ rewEmoValence*block_trial_number_c + (1+block_trial_number_c|subject)+(1|choiceImage),data=d_graph_emotion, family=binomial,glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)))
summary(m_emotion_val)
emmeans::emmeans (m_emotion_val, pairwise ~ rewEmoValence)
emmeans::emmeans (m_emotion_val, pairwise ~ rewEmoValence | block_trial_number_c, at = list(block_trial_number_c = .5 + 4:6))

plot_model(m_emotion_val, type = "pred", terms = c("block_trial_number_c", "rewEmoValence"))

m_emotion_val_h.e <- glmer(max_reward_choice ~ rewEmoHAPPY_EX*block_trial_number_c + (1+block_trial_number_c|subject)+(1|choiceImage),data=d_graph_emotion, family=binomial,glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)))
summary(m_emotion_val_h.e)

plot_model(m_emotion_val_h.e, type = "pred", terms = c("block_trial_number_c", "rewEmoHAPPY_EX"))


m_emotion_spec_emo <- glmer(max_reward_choice ~ rewEmotion_inclModel*block_trial_number_c + (1+block_trial_number_c|subject)+(1|choiceImage),data=d_graph_emotion, family=binomial,glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)))
summary(m_emotion_spec_emo)

plot_model(m_emotion_spec_emo, type = "pred", terms = c("block_trial_number_c", "rewEmotion_inclModel"))

```

## Consistency

#### broad emotion
```{r}
d_nameability <- read_csv("emogo-combined-nameability.csv") %>%
  mutate(model_emotion = image) %>%
  separate(image, into = c("model", "emotion"), sep = "_", convert = TRUE) %>%
  mutate(`modal response (32 models)` =                          
           ifelse(grepl('calm',modal_response) |
                    grepl('neut',modal_response),"calm, neutral",  ifelse(grepl('happ',modal_response),"happiness",
                           ifelse(grepl('sad',modal_response),"sad",
                           ifelse(grepl('fear',modal_response),"fear, scared",
                           ifelse(grepl('shock',modal_response) |
                    grepl('surp',modal_response),"shock, surprise",modal_response)))))) %>%
  mutate(emo_name = ifelse(grepl('AO',emotion),"angry",
                           ifelse(grepl('CC',emotion),"calm",
                           ifelse(grepl('DO',emotion),"disgust",
                           ifelse(grepl('FO',emotion),"fear",
                           ifelse(grepl('HE',emotion),"exuberent",
                           ifelse(grepl('HO',emotion),"happy",
                           ifelse(grepl('SC',emotion),"sad","surprise")))))))) %>%
  mutate(rewEmotion = emo_name)

ggplot(d_nameability, aes(simpson_diversity, fill = emo_name)) +
   geom_histogram() +
    #facet_grid(~ emo_name)+
  theme_bw()+labs(x="Consistency \n(Simpson Diversity)",y="Count", title = " ")+
  theme(panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.line = element_line(colour = "black"), legend.key.size = unit(1, "cm"),text=element_text(size=24, family="Times"))+
  guides(linetype=guide_legend(override.aes=list(alpha=1)))

ggplot(d_nameability, aes(simpson_diversity, after_stat(density), colour = emo_name)) +
  geom_freqpoly()

ggplot(data = d_nameability) + 
  geom_bar(mapping = aes(x = emo_name, fill = `modal response (32 models)`))+
  theme_bw()+labs(x="Emotion Signal",y="Modal Response (per Image)", title = " ")+
  theme(panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.line = element_line(colour = "black"), legend.key.size = unit(1, "cm"),text=element_text(size=24, family="Times"))+
  guides(linetype=guide_legend(override.aes=list(alpha=1)))

d_name_join <- d_nameability %>%
  select(rewEmotion, simpson_diversity) %>%
  group_by(rewEmotion) %>%
  summarise(avg_simpson_diversity = mean(simpson_diversity)) %>%
  right_join(d_graph_emotion) %>%
  filter(structure_condition_c == .5)

m_consistency <- glmer(max_reward_choice ~ block_trial_number_c*avg_simpson_diversity + (1+block_trial_number_c|subject)+(1|choiceImage),data=d_name_join, family=binomial,glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)))
summary(m_consistency)

sjPlot::plot_model(m_consistency, type = "pred", terms = c("block_trial_number_c", "avg_simpson_diversity"))
```

#### specific models
```{r}
### need to get simpson diversity for specific model
d_nameability_sub <- d_nameability %>%
  mutate(rewImage = model_emotion) %>%
  select(rewImage, simpson_diversity)

d_graph_emotion_sub <- d_graph_emotion %>%
  select(subject, structure_condition, structure_condition_c, block_trial_number, block_trial_number_c, choiceEmotion, choiceModel, reward_score_unadjusted, task_version, max_reward_choice, image1:image4, rewards_unadjusted) %>%
  unite(model_emotion, choiceModel, choiceEmotion, sep = "_")%>%
  separate(rewards_unadjusted, c("rew_image1", "rew_image2", "rew_image3", "rew_image4"), sep = ",") %>%
  mutate(rewImage = ifelse(grepl(8, rew_image1), image1,
                           ifelse(grepl(8, rew_image2), image2,
                                  ifelse(grepl(8, rew_image3), image3,
                                         ifelse(grepl(8, rew_image4), image4,"FAIL"))))) %>%
  separate(rewImage, c("junk", "rewImage"), sep = "/") %>%
  separate(rewImage, c("rewImage", "junkToo"), sep = ".j") %>%
  select(-junk, -junkToo) %>%
  left_join(d_nameability_sub)
  

m_cons_spec <- glmer(max_reward_choice ~ structure_condition_c*block_trial_number_c*simpson_diversity + (1+block_trial_number_c|subject),data=d_graph_emotion_sub, family=binomial,glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)))
summary(m_cons_spec)

sjPlot::plot_model(m_cons_spec, type = "pred", terms = c("block_trial_number_c", "simpson_diversity", "structure_condition_c"))

hist(d_graph_emotion_sub$simpson_diversity)

m_cons_spec_emo <- glmer(max_reward_choice ~ block_trial_number_c*simpson_diversity + (1+block_trial_number_c|subject),data=filter(d_graph_emotion_sub, structure_condition_c == .5), family=binomial,glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)))
summary(m_cons_spec_emo)

sjPlot::plot_model(m_cons_spec_emo, type = "pred", terms = c("block_trial_number_c", "simpson_diversity"))


####
color1 <- "#2B959A"
color2 <-"#D6692A"

median(d_graph_emotion_sub$simpson_diversity, na.rm = TRUE)
d_graph_emotion_sub$simpson_diversity_split <- ifelse(d_graph_emotion_sub$simpson_diversity < .25, "low", "high")

d_graph <- d_graph_emotion_sub %>%
  drop_na(simpson_diversity_split)

ggplot(d_graph,aes(block_trial_number,max_reward_choice,color = structure_condition, linetype = simpson_diversity_split))+
  geom_jitter(height = .005, alpha = .05)+
  geom_smooth(method = "loess")+
  theme_bw()+labs(x="Trial Number",y="Chose Best Option", title = " ")+
  scale_color_manual(values=c(color1, color2), labels=c("Emotion","Model"),name="Structure Condition")+
  scale_linetype_manual(values=c("solid", "dashed"), labels=c("High","Low"),name=" Label Consistency \nAcross Participants") +
  theme(panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.line = element_line(colour = "black"), legend.key.size = unit(1, "cm"),text=element_text(size=20, family="Times"))

```


## ind diffs
```{r}
d_match_pers <- read_csv("data/emogo-spark-personality-alldata.csv") %>%
  select(subject, workerId) %>%
  distinct()

# at some point need to figure out why these are different numbers
length(unique(d_match_pers$workerId))
length(unique(d_match_pers$subject))

d_match_psych <- read_csv("data/emogo-spark-psychopathology-alldata.csv") %>%
  select(subject, workerId) %>%
  distinct()

length(unique(d_match_psych$workerId))
length(unique(d_match_psych$subject))

d_match <- d_match_psych %>%
  full_join(d_match_pers)

d_pers <- read_csv("Qualtrics_data/SPARK_P_Emogo_CleanConstructsOnly.csv")

d_psych <- read_csv("Qualtrics_data/SPARK_Psycho_Emogo_ConstructsOnly.csv")

d_join <- d_pers %>%
  full_join(d_psych) %>%
  full_join(d_match) %>%
  select(subject, P_STAR:P_TF_BOLD_SCORE)

d_combo <- d_graph   %>%
  filter(task_version == "spark-personality" | task_version == "spark-psychopathology") %>%
  select(subject, task_version, block_trial_number, block_trial_number_c, structure_condition, structure_condition_c, max_reward_choice, choiceImage) %>%
  left_join(d_join) 
```

### center continuous vars
```{r}
d_combo <- d_combo %>%
  mutate(P_STAR_STS_c = P_STAR_STS-mean(P_STAR_STS, na.rm = TRUE),
         P_STAR_SA_c = P_STAR_SA - mean(P_STAR_SA, na.rm =TRUE),
         P_NEO_AGREE_c = P_NEO_AGREE - mean(P_NEO_AGREE, na.rm =TRUE),
         P_NEO_OPEN_c = P_NEO_OPEN - mean(P_NEO_OPEN, na.rm =TRUE),
         P_NEO_NEURO_c = P_NEO_NEURO - mean(P_NEO_NEURO, na.rm =TRUE),
         P_NEO_EXTRA_c = P_NEO_EXTRA - mean(P_NEO_EXTRA, na.rm =TRUE),
         P_FFI_CONSCI_c = P_FFI_CONSCI - mean(P_FFI_CONSCI, na.rm =TRUE),
         P_PID_ANTAG_DOMAIN_c = P_PID_ANTAG_DOMAIN - mean(P_PID_ANTAG_DOMAIN, na.rm = TRUE),
         P_TRIPM_MEAN_c = P_TRIPM_MEAN - mean(P_TRIPM_MEAN, na.rm = TRUE),
         P_SRP_c = P_SRP - mean(P_SRP, na.rm = TRUE),
         P_SRP_AF_c = P_SRP_AF - mean(P_SRP_AF, na.rm = TRUE))


d_combo_pers <- d_combo %>%
  filter(task_version == "spark-personality")
length(unique(d_combo_pers$subject))

d_combo_psych <- d_combo %>%
  filter(task_version == "spark-psychopathology")
length(unique(d_combo_psych$subject))


d_combo_social <- d_combo %>%
  filter(structure_condition_c == .5)

d_agg <- d_combo_social %>%
  group_by(subject) %>%
  summarise(mean_max = mean(max_reward_choice, na.rm = TRUE)) %>%
  left_join(d_join) %>%
  select(-subject)

d_table <- as_tibble(corx::corx(d_agg))

```


### ind diffs models

#### SRP
```{r}
m <- glmer(max_reward_choice ~ structure_condition_c*block_trial_number_c*P_SRP_AF_c + (1|subject),data=d_combo_pers, family=binomial,glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)))
summary(m)

sjPlot::plot_model(m, type = "pred", terms = c("block_trial_number_c", "P_SRP_AF_c", "structure_condition_c"))

####
color1 <- "#2B959A"
color2 <-"#D6692A"

median(d_combo_pers$P_SRP_AF, na.rm = TRUE)
d_combo_pers$P_SRP_AF_split <- ifelse(d_combo_pers$P_SRP < 2, "high", "low")

d_combo_pers_graph <- d_combo_pers %>%
  drop_na(P_SRP_AF_split)

srp_graph <- ggplot(d_combo_pers_graph,aes(block_trial_number,max_reward_choice,color = structure_condition, linetype = P_SRP_AF_split))+
  geom_jitter(height = .005, alpha = .05)+
  geom_smooth(method = "loess")+
  theme_bw()+labs(x="Trial Number",y="Chose Best Option", title = "Affect. Functioning (SRP-AF)")+
  scale_color_manual(values=c(color1, color2), labels=c("Emotion","Model"),name="Structure Condition")+
  scale_linetype_manual(values=c("solid", "dashed"), labels=c("High","Low"),name=" ") +
  theme(panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.line = element_line(colour = "black"), legend.key.size = unit(1, "cm"),text=element_text(size=20, family="Times"))

```

#### personality models
```{r}
## openness
m_open <- glmer(max_reward_choice ~ structure_condition_c*block_trial_number_c*P_NEO_OPEN_c + (1|subject),data=d_combo_pers, family=binomial,glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)))
summary(m_open)

sjPlot::plot_model(m_open, type = "pred", terms = c("block_trial_number_c", "P_NEO_OPEN_c", "structure_condition_c"))

## agreeableness
m_agree <- glmer(max_reward_choice ~ structure_condition_c*block_trial_number_c*P_NEO_AGREE_c + (1|subject),data=d_combo_pers, family=binomial,glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)))
summary(m_agree)

sjPlot::plot_model(m_agree, type = "pred", terms = c("block_trial_number_c", "P_NEO_AGREE_c", "structure_condition_c"))

## extraversion
m_extra <- glmer(max_reward_choice ~ structure_condition_c*block_trial_number_c*P_NEO_EXTRA_c + (1|subject),data=d_combo_pers, family=binomial,glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)))
summary(m_extra)

sjPlot::plot_model(m_extra, type = "pred", terms = c("block_trial_number_c", "P_NEO_EXTRA_c", "structure_condition_c"))

## neuroticism
m_neuro <- glmer(max_reward_choice ~ structure_condition_c*block_trial_number_c*P_NEO_NEURO_c + (1|subject),data=d_combo_pers, family=binomial,glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)))
summary(m_neuro)

sjPlot::plot_model(m_neuro, type = "pred", terms = c("block_trial_number_c", "P_NEO_NEURO_c", "structure_condition_c"))

## conscientiousness
m_consci <- glmer(max_reward_choice ~ structure_condition_c*block_trial_number_c*P_FFI_CONSCI_c + (1|subject),data=d_combo_pers, family=binomial,glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)))
summary(m_consci)

sjPlot::plot_model(m_consci, type = "pred", terms = c("block_trial_number_c", "P_FFI_CONSCI_c", "structure_condition_c"))


#### agreeable

hist(d_combo_pers$P_NEO_AGREE, na.rm = TRUE)

median(d_combo_pers$P_NEO_AGREE, na.rm = TRUE)
d_combo_pers$P_NEO_AGREE_split <- ifelse(d_combo_pers$P_NEO_AGREE < 2.7, "low", "high")

d_combo_pers_graph <- d_combo_pers %>%
  drop_na(P_NEO_AGREE_split)

agree_graph <- ggplot(d_combo_pers_graph,aes(block_trial_number,max_reward_choice,color = structure_condition, linetype = P_NEO_AGREE_split))+
  geom_jitter(height = .005, alpha = .05)+
  geom_smooth(method = "loess")+
  theme_bw()+labs(x="Trial Number",y="Chose Best Option", title = "Agreeableness (NEO-FFI)")+
  scale_color_manual(values=c(color1, color2), labels=c("Emotion","Model"),name="Structure Condition")+
  scale_linetype_manual(values=c("solid", "dashed"), labels=c("High","Low"),name=" ") +
  theme(panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.line = element_line(colour = "black"), legend.key.size = unit(1, "cm"),text=element_text(size=20, family="Times"))

#### openness

hist(d_combo_pers$P_NEO_OPEN, na.rm = TRUE)

median(d_combo_pers$P_NEO_OPEN, na.rm = TRUE)
d_combo_pers$P_NEO_OPEN_split <- ifelse(d_combo_pers$P_NEO_OPEN < 2.6, "low", "high")

d_combo_pers_graph <- d_combo_pers %>%
  drop_na(P_NEO_OPEN_split)

ggplot(d_combo_pers_graph,aes(block_trial_number,max_reward_choice,color = structure_condition, linetype = P_NEO_OPEN_split))+
  geom_jitter(height = .005, alpha = .05)+
  geom_smooth(method = "loess")+
  theme_bw()+labs(x="Trial Number",y="Chose Best Option")+
  scale_color_manual(values=c(color1, color2), labels=c("Emotion","Model"),name="Structure Condition")+
  scale_linetype_manual(values=c("solid", "dashed"), labels=c("High","Low"),name="Openness") +
  theme(panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.line = element_line(colour = "black"), legend.key.size = unit(1, "cm"),text=element_text(size=20, family="Times"))

#### extraversion

hist(d_combo_pers$P_NEO_EXTRA, na.rm = TRUE)

median(d_combo_pers$P_NEO_EXTRA, na.rm = TRUE)
d_combo_pers$P_NEO_EXTRA_split <- ifelse(d_combo_pers$P_NEO_EXTRA < 2, "low", "high")

d_combo_pers_graph <- d_combo_pers %>%
  drop_na(P_NEO_EXTRA_split)

ggplot(d_combo_pers_graph,aes(block_trial_number,max_reward_choice,color = structure_condition, linetype = P_NEO_EXTRA_split))+
  geom_jitter(height = .005, alpha = .05)+
  geom_smooth(method = "loess")+
  theme_bw()+labs(x="Trial Number",y="Chose Best Option")+
  scale_color_manual(values=c(color1, color2), labels=c("Emotion","Model"),name="Structure Condition")+
  scale_linetype_manual(values=c("solid", "dashed"), labels=c("High","Low"),name="Extraversion") +
  theme(panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.line = element_line(colour = "black"), legend.key.size = unit(1, "cm"),text=element_text(size=20, family="Times"))


#### neuroticism

hist(d_combo_pers$P_NEO_NEURO, na.rm = TRUE)

median(d_combo_pers$P_NEO_NEURO, na.rm = TRUE)
d_combo_pers$P_NEO_NEURO_split <- ifelse(d_combo_pers$P_NEO_NEURO < 1.96, "low", "high")

d_combo_pers_graph <- d_combo_pers %>%
  drop_na(P_NEO_NEURO_split)

ggplot(d_combo_pers_graph,aes(block_trial_number,max_reward_choice,color = structure_condition, linetype = P_NEO_NEURO_split))+
  geom_jitter(height = .005, alpha = .05)+
  geom_smooth(method = "loess")+
  theme_bw()+labs(x="Trial Number",y="Chose Best Option")+
  scale_color_manual(values=c(color1, color2), labels=c("Emotion","Model"),name="Structure Condition")+
  scale_linetype_manual(values=c("solid", "dashed"), labels=c("High","Low"),name="Neuroticism") +
  theme(panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.line = element_line(colour = "black"), legend.key.size = unit(1, "cm"),text=element_text(size=20, family="Times"))


#### conscientiousness

hist(d_combo_pers$P_FFI_CONSCI, na.rm = TRUE)

median(d_combo_pers$P_FFI_CONSCI, na.rm = TRUE)
d_combo_pers$P_FFI_CONSCI_split <- ifelse(d_combo_pers$P_FFI_CONSCI < 2.83, "low", "high")

d_combo_pers_graph <- d_combo_pers %>%
  drop_na(P_FFI_CONSCI_split)

ggplot(d_combo_pers_graph,aes(block_trial_number,max_reward_choice,color = structure_condition, linetype = P_FFI_CONSCI_split))+
  geom_jitter(height = .005, alpha = .05)+
  geom_smooth(method = "loess")+
  theme_bw()+labs(x="Trial Number",y="Chose Best Option")+
  scale_color_manual(values=c(color1, color2), labels=c("Emotion","Model"),name="Structure Condition")+
  scale_linetype_manual(values=c("solid", "dashed"), labels=c("High","Low"),name="Conscientiousness") +
  theme(panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.line = element_line(colour = "black"), legend.key.size = unit(1, "cm"),text=element_text(size=20, family="Times"))



```
#### P_PID_ANTAG_DOMAIN

```{r}
## P_PID_ANTAG_DOMAIN
d_combo_pers$P_PID_ANTAG_DOMAIN_c_scale <- d_combo_pers$P_PID_ANTAG_DOMAIN_c/2
d_combo_pers$block_trial_number_c_scale <- d_combo_pers$block_trial_number_c/2

m_P_PID_ANTAG_DOMAIN <- glmer(max_reward_choice ~ structure_condition_c*block_trial_number_c_scale*P_PID_ANTAG_DOMAIN_c_scale + (1|subject),data=d_combo_pers, family=binomial,glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)))
summary(m_P_PID_ANTAG_DOMAIN)

sjPlot::plot_model(m_P_PID_ANTAG_DOMAIN, type = "pred", terms = c("block_trial_number_c_scale", "P_PID_ANTAG_DOMAIN_c_scale", "structure_condition_c"))

##
hist(d_combo_pers$P_PID_ANTAG_DOMAIN, na.rm = TRUE)

median(d_combo_pers$P_PID_ANTAG_DOMAIN, na.rm = TRUE)
d_combo_pers$P_PID_ANTAG_DOMAIN_split <- ifelse(d_combo_pers$P_PID_ANTAG_DOMAIN < 2, "low", "high")

d_combo_pers_graph <- d_combo_pers %>%
  drop_na(P_PID_ANTAG_DOMAIN_split)

antag_graph <- ggplot(d_combo_pers_graph,aes(block_trial_number,max_reward_choice,color = structure_condition, linetype = P_PID_ANTAG_DOMAIN_split))+
  geom_jitter(height = .005, alpha = .05)+
  geom_smooth(method = "loess")+
  theme_bw()+labs(x="Trial Number",y="Chose Best Option", title = "Antagonism (PID)")+
  scale_color_manual(values=c(color1, color2), labels=c("Emotion","Model"),name="Structure Condition")+
  scale_linetype_manual(values=c("solid", "dashed"), labels=c("High","Low"),name=" ") +
  theme(panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.line = element_line(colour = "black"), legend.key.size = unit(1, "cm"),text=element_text(size=20, family="Times"))

```
#### composite fig
```{r}
ggpubr::ggarrange(srp_graph, agree_graph, antag_graph,
          ncol = 2, nrow = 2, common.legend = TRUE, font.label = list(size = 14))
```


#### P_TRIPM_MEAN

```{r}
## P_TRIPM_MEAN
m_P_TRIPM_MEAN <- glmer(max_reward_choice ~ structure_condition_c*block_trial_number_c*P_TRIPM_MEAN_c + (1|subject),data=d_combo_psych, family=binomial,glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)))
summary(m_P_TRIPM_MEAN)

sjPlot::plot_model(m_P_TRIPM_MEAN, type = "pred", terms = c("block_trial_number_c", "P_TRIPM_MEAN_c", "structure_condition_c"))

##
hist(d_combo_pers$P_PID_ANTAG_DOMAIN, na.rm = TRUE)

median(d_combo_pers$P_PID_ANTAG_DOMAIN, na.rm = TRUE)
d_combo_pers$P_PID_ANTAG_DOMAIN_split <- ifelse(d_combo_pers$P_PID_ANTAG_DOMAIN < 2, "low", "high")

d_combo_pers_graph <- d_combo_pers %>%
  drop_na(P_PID_ANTAG_DOMAIN_split)

ggplot(d_combo_pers_graph,aes(block_trial_number,max_reward_choice,color = structure_condition, linetype = P_PID_ANTAG_DOMAIN_split))+
  geom_jitter(height = .005, alpha = .05)+
  geom_smooth(method = "loess")+
  theme_bw()+labs(x="Trial Number",y="Chose Best Option")+
  scale_color_manual(values=c(color1, color2), labels=c("Emotion","Model"),name="Structure Condition")+
  scale_linetype_manual(values=c("solid", "dashed"), labels=c("High","Low"),name="Antagonism \n(PID)") +
  theme(panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.line = element_line(colour = "black"), legend.key.size = unit(1, "cm"),text=element_text(size=20, family="Times"))

```


